WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2014-07-19 ms.tex
Apply \mathcal to some symbols

We can compute the Fisher matrix elements for the autocorrelation likelihood given by \Eref{eq:autocor-likelihood}, with detector subscript suppressed:
%
\begin{eqnarray}
    \nonumber
    \mathcal{I}_{\rho\rho} &=& 1 \\
    \nonumber
    \mathcal{I}_{\rho\gamma} &=& 0 \\
    \nonumber
    \mathcal{I}_{\rho\tau} &=& 0 \\
    \label{eq:fisher-autocor-gamma-gamma}
    \mathcal{I}_{\gamma\gamma} &=& \rho^2
        \int_{-T}^T \left|a(t)\right|^2 w(t; \rho) dt \\
    \label{eq:fisher-autocor-tau-tau}
    \mathcal{I}_{\tau\tau} &=& -\rho^2
        \int_{-T}^T \Re\left[a^*(t) a''(t)\right] w(t; \rho) dt \\
    \label{eq:fisher-autocor-gamma-tau}
    \mathcal{I}_{\gamma\tau} &=& -\rho^2
        \int_{-T}^T \Im\left[a^*(t) a'(t)\right] w(t; \rho) dt \\
    \nonumber\textrm{where} && \\
    w(t; \rho) &=& \frac{
        \displaystyle
        \exp\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right]
        \left(
        I_0\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right] +
        I_1\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right]
        \right)
    }{
        \displaystyle
        2 \int_{-T}^T
        \exp\left[\frac{\rho^2}{4}\left|a(t')\right|^2\right]
        I_0\left[\frac{\rho^2}{4}\left|a(t')\right|^2\right]
        dt'
    }.
\end{eqnarray}
%
Matrix elements that are not listed have values that are implied by the symmetry of the Fisher matrix. Note that the minus signs are correct but a little confusing: despite them, ${I}_{\gamma\gamma}, {I}_{\tau\tau} \geq 0$ and ${I}_{\gamma\tau} \leq 0$. The time integration limits $[-T, T]$ constitute a flat prior on arrival time, the time coincidence window between detectors.

>>>>

We can compute the Fisher matrix elements for the autocorrelation likelihood given by \Eref{eq:autocor-likelihood}, with detector subscript suppressed:
%
\begin{eqnarray}
    \nonumber
    \mathcal{I}_{\rho\rho} &=& 1 \\
    \nonumber
    \mathcal{I}_{\rho\gamma} &=& 0 \\
    \nonumber
    \mathcal{I}_{\rho\tau} &=& 0 \\
    \label{eq:fisher-autocor-gamma-gamma}
    \mathcal{I}_{\gamma\gamma} &=& \rho^2
        \int_{-T}^T \left|a(t)\right|^2 w(t; \rho) dt \\
    \label{eq:fisher-autocor-tau-tau}
    \mathcal{I}_{\tau\tau} &=& -\rho^2
        \int_{-T}^T \Re\left[a^*(t) a''(t)\right] w(t; \rho) dt \\
    \label{eq:fisher-autocor-gamma-tau}
    \mathcal{I}_{\gamma\tau} &=& -\rho^2
        \int_{-T}^T \Im\left[a^*(t) a'(t)\right] w(t; \rho) dt \\
    \nonumber\textrm{where} && \\
    w(t; \rho) &=& \frac{
        \displaystyle
        \exp\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right]
        \left(
        I_0\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right] +
        I_1\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right]
        \right)
    }{
        \displaystyle
        2 \int_{-T}^T
        \exp\left[\frac{\rho^2}{4}\left|a(t')\right|^2\right]
        I_0\left[\frac{\rho^2}{4}\left|a(t')\right|^2\right]
        dt'
    }.
\end{eqnarray}
%
Matrix elements that are not listed have values that are implied by the symmetry of the Fisher matrix. Note that the minus signs are correct but a little confusing: despite them, $\mathcal{I}_{\gamma\gamma}, \mathcal{I}_{\tau\tau} \geq 0$ and $\mathcal{I}_{\gamma\tau} \leq 0$. The time integration limits $[-T, T]$ constitute a flat prior on arrival time, the time coincidence window between detectors.
